Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-15 journal paper/content/sec-bg.tex
Full draft of the bg.

The three classes of algorithms are well-separated in terms of \BIR, much like they are in terms of regret.

\begin{itemize}
\item \DynGreedy has at least a constant \BIR for many reasonable priors (where the constant can depend on $K$ and the prior, but not on $t$). The reason and the proof are exactly the same as for regret.

\item Exploration-separating algorithms can achieve
    $\BIR(t) = \tildeO(t^{-1/3})$
for all priors, \eg by using Epsilon-Greedy with exploration probability $\eps_t = t^{-1/3}$ in each round $t$. 
The $t^{-1/3}$ rate is the best possible, in the sense that

\ascomment{stopped here.}

\item Adaptive-exploration algorithms can have an even better rate
    $\BIR(n) \sim n^{-1/3}$
for all priors. 
\end{itemize}

Both rates are up to $\log(n)$ factors, and are the best possible \BIR rates that can be achieved for all priors.
\ascomment{stopped here.}

>>>>

The three classes of algorithms are well-separated in terms of \BIR, much like they are in terms of regret. (The precise regret rates are listed below only to illustrate this point.)
\begin{itemize}
\item \DynGreedy has at least a constant \BIR for many reasonable priors (where the constant can depend on $K$ and the prior, but not on $t$). The reason and the proof are exactly the same as for regret.

\item Exploration-separating algorithms can achieve
    $\BIR(t) = \tildeO\rbr{t^{-1/3}}$
for all priors, \eg by using Epsilon-Greedy with exploration probability $\eps_t = t^{-1/3}$ in each round $t$.
The $t^{-1/3}$ rate is the best possible in the worst case, in the following sense: 
    $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$ 
for all $t$ and some $\gamma>0$,
over all problem instances, then $\gamma\geq \nicefrac{1}{3}$. This is by \eqref{eq:bg-BReg} and the fact that $\BReg(T)\geq \Omega(T^{2/3})$ in the worst case. (The latter follows from the `frequentist" lower bound in \citet{MechMAB-ec09}.)

\item Adaptive-exploration algorithms \emph{can} have an even better regret rate: $\BIR(t) = \tildeO\rbr{ t^{-1/2} } $, \eg this holds for Successive Elimination \citep{EvenDar-icml06}. Any optimal MAB algorithm such as Thompson Sampling and UCB1 enjoys this regret rate ``on average", because it satisfies 
        $\BReg(T)\leq \tildeO(sqrt{T})$.
    Put differently, if such algorithm satisfies 
        $\BIR(t) = \tildeO\rbr{t^{-\gamma}}$
    for all $t$ and some $\gamma>0$, then $\gamma \leq \nicefrac{1}{2}$.
    That said, a uniform upper bound on $\BIR$ of Thompson Sampling or UCB1 is not known, to the best of our knowledge.

\end{itemize}

This theoretical intuition is supported by plots in 
Figure~\ref{relative_rep_plots} and Appendix~\ref{app:isol}.
